Globally-centered autocovariances in MCMC

### 2020-09-02 Paper/main.tex
Chal chale apne ghar

We can break $\hat{\Gamma}_{G,s}$ into four parts for all $k \geq 1$ as:
%
\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\ 
    & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. Under the assumption of stationarity, we will study the expectations of each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

@@

By \cite[Proposition 1]{song1995optimal},
\[
\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})\,.
\]
As a consequence, we get the result 
\[
 \E \left[\hat{\Gamma}_{G,s}(k) \right] =  \left(1- \dfrac{\abs{k}}{n}\right)\left( \Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} \right) + o(n^{-1})\,.
\]
% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
Although this completes the proof of Theorem~\ref{th:G-ACF_bias}, we will require the following decomposition
 \begin{equation} \label{eq:G-ACF_expec_breakdown}
     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2\,.
 \end{equation}
%
where,
\begin{align*}
    O_1 &= -\dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
\end{align*}
%
% Here $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \to 0 \textrm{ and } O_2 = {\mathcal{O}}(1/n) \to 0$ as $n \to \infty$. For a diagonal element of $\Gamma$,
% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
%
% \begin{align*}
% & \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
% & = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
% \end{align*}
% Note that $ \hat{\Gamma}_{G,s}(k)$ is less negatively biased as compared to $\hat{\Gamma}_s(k)$. In the presence of positive correlation, the leftover $o(n^{-1})$ term is positive which further counters the negative bias of $\hat{\Gamma}_{G,s}(k)$.

@@

\subsection{Strong consistency argument} \label{appendix:strong_consis}

@@

\begin{lemma} \label{lemma:G-SVE_breakdown}
Let Assumption~\ref{ass:lag_window} holds, then for the G-SV estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
\[
|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,,
\]
where for some constant $C$,
\begin{align*}
    g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
\end{align*}
\end{lemma}

@@

\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{SV}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}

@@

% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$. We are interested in finding the asymptotic bias here. Therefore we can write the expectation of replicated autocovariance in form of 
By Equation~\ref{eq:G-ACF_expec_breakdown},
%\begin{align*}
%\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right]
% &  = \left(1- \dfrac{k}{n}\right)\Upsilon(k) - \dfrac{k}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m} \\
% & = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + \mathcal{O} \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
% \end{align*}
%
%
\[
\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + O_1 + O_2    \,.
\]
%
where both $O_1 \textrm{ and } O_2$ are the small order terms where $O_1 = n^{-1}\abs{k} \mathcal{O}(n^{-1}) \text{ and } O_2 = \mathcal{O}(n^{-1})$. By our assumptions, $\sum_{k=-\infty}^{\infty}\Upsilon(k) < \infty$.  
For a truncation point $b_n$, $w(k/b_n)=0$ for all $\abs{k} > b_n$. Therefore, SV estimator can be written as a weighted sum of estimated autocovariances from lag $-n+1$ to $n-1$. Consider the G-SV estimator,
\begin{align*}
 \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{k}{n}\right)\Upsilon(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k)\right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\ 
    & = P_1 + P_2\,,
\end{align*}
%
where 
\begin{align*}
    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Upsilon(k) \textrm{ and }\\   
    P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
\end{align*}

%
Similar to \cite{hannan:1970}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
\begin{equation}
\label{eq:P1_decomp}
P_1 = -\sum_{\abs{k}\geq n}\Upsilon(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{n}\right)\right)\Upsilon(k)\,.  
\end{equation}
%
We deal with the three subterms of term $P_1$ individually. First,
%    
\begin{align*}
 {-\sum_{\abs{k}\geq n}\Upsilon(k)} &\leq  \sum_{\abs{k}\geq n} \abs{\dfrac{k}{n}}^q   \Upsilon(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{k\geq n}\abs{k}^q  \Upsilon(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
\end{align*}
%
since $\sum_{\abs{k}\geq n}\abs{k}^q \Upsilon(k)  < \infty$. Next,
%
\begin{align*}
 \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}\abs{k} \Upsilon(k)  \,.
\end{align*}
For $q\geq 1$,
\begin{align*}
\dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k}  \Upsilon(k) &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k}^q  \Upsilon(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} c\sum_{k = -n+1}^{n-1}\abs{k}^q  \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
\end{align*}

@@

  Finally, we will solve for $P_2$. Note that $O_2$ is independent of $k$. We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$. We will find an upper bound and prove that it is $o\left(b_n^{-q}\right)$:
  \begin{align*}
      &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{k}{b_n}\right)( O_1 + O_2) \\
      & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
 \end{align*}

>>>>

We can break $\hat{\Gamma}_{G,s}$ into four parts for all $k \geq 1$ as:
%
\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\ 
    & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. Under the assumption of stationarity, we will study the expectations of each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

@@

By \cite[Proposition 1]{song1995optimal},
\[
\Var(\bar{X}_s) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})\,.
\]
As a consequence, we get the result 
\[
 \E \left[\hat{\Gamma}_{G,s}(k) \right] =  \left(1- \dfrac{\abs{k}}{n}\right)\left( \Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} \right) + o(n^{-1})\,.
\]
% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
Although this completes the proof of Theorem~\ref{th:G-ACF_bias}, we will require the following decomposition
 \begin{equation} \label{eq:G-ACF_expec_breakdown}
     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2\,.
 \end{equation}
%
where,
\begin{align*}
    O_1 &= -\dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] + o(n^{-2})\, ,\\
    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
\end{align*}
%
% Here $O_1 = (\abs{k}/n)\mathcal{O}(1/n) \to 0 \textrm{ and } O_2 = {\mathcal{O}}(1/n) \to 0$ as $n \to \infty$. For a diagonal element of $\Gamma$,
% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
%
% \begin{align*}
% & \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
% & = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)^{ii}\right] - \dfrac{\Var(\bar{X}_1)^{ii}}{m}\,.
% \end{align*}
% Note that $ \hat{\Gamma}_{G,s}(k)$ is less negatively biased as compared to $\hat{\Gamma}_s(k)$. In the presence of positive correlation, the leftover $o(n^{-1})$ term is positive which further counters the negative bias of $\hat{\Gamma}_{G,s}(k)$.

@@

\subsection{Strong consistency of G-SV estimator} \label{appendix:strong_consis}

@@

\begin{lemma} \label{lemma:G-SVE_breakdown}
Let Assumption~\ref{ass:lag_window} holds, then for the G-SV estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
\[
|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,,
\]
where for some constant $C$,
\begin{align*}
    g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0 \quad \text{as }n \to \infty\,.
\end{align*}
\end{lemma}

@@

\left|\hat{\Sigma}_{G}^{ij} - \Sigma^{ij} \right| & = \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} + N_1 + N_2 + M_1 + M_2 \right|  \leq \left| \hat{\Sigma}_{A}^{ij} - \Sigma^{ij} \right| +  \left| N_1 \right| +  \left|N_2 \right| + \left| M_1 + M_2 \right| \numberthis \label{eq:G-SVE_full_decomp}

@@

% \begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
% The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$. We are interested in finding the asymptotic bias here. Therefore we can write the expectation of replicated autocovariance in form of 
By Equation~\ref{eq:G-ACF_expec_breakdown},
%\begin{align*}
%\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right]
% &  = \left(1- \dfrac{k}{n}\right)\Upsilon(k) - \dfrac{k}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Upsilon(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m} \\
% & = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + \mathcal{O} \left(n^{-1} \right)  \numberthis \label{eq:G-_bias2}  \,.
% \end{align*}
%
%
\[
\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Upsilon(k) + O_1 + O_2    \,.
\]
%
where both $O_1 \textrm{ and } O_2$ are the small order terms where $O_1 = n^{-1}\abs{k} \mathcal{O}(n^{-1}) \text{ and } O_2 = \mathcal{O}(n^{-1})$. By our assumptions, $\sum_{k=-\infty}^{\infty}\Upsilon(k) < \infty$.  
For a truncation point $b_n$, $w(k/b_n)=0$ for all $\abs{k} > b_n$. Therefore, SV estimator can be written as a weighted sum of estimated autocovariances from lag $-n+1$ to $n-1$. Consider the G-SV estimator,
\begin{align*}
 \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] & = \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Upsilon}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{k}{n}\right)\Upsilon(k) + O_1 + O_2 \right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k)\\
    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k)\right]  - \sum_{k=-\infty}^{\infty}\Upsilon(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)  (O_1 + O_2) \right] \\ 
    & = P_1 + P_2\,, \numberthis \label{eq:bias_gsve}
\end{align*}
%
where 
\begin{align*}
    P_1 &= \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{\abs{k}}{n}\right)\Upsilon(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Upsilon(k) \textrm{ and }\\   
    P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
\end{align*}
%
%
Similar to \cite{hannan:1970}, we break $P_1$ into three parts. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for every $(i,j)$th element of the matrix $A$. Consider,
\begin{equation}
\label{eq:P1_decomp}
P_1 = -\sum_{\abs{k}\geq n}\Upsilon(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{n}\right)\right)\Upsilon(k)\,.  
\end{equation}
%
We deal with the three subterms of term $P_1$ individually. First,
%    
\begin{align*}
 {-\sum_{\abs{k}\geq n}\Upsilon(k)} &\leq  \sum_{\abs{k}\geq n} \abs{\dfrac{k}{n}}^q   \Upsilon(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{k\geq n}\abs{k}^q  \Upsilon(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
\end{align*}
%
since $\sum_{\abs{k}\geq n}\abs{k}^q \Upsilon(k)  < \infty$. Next,
%
\begin{align*}
 \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{\abs{k}}{n}\Upsilon(k)   &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k} \Upsilon(k)  \,.
\end{align*}
For $q\geq 1$,
\begin{align*}
\dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k}  \Upsilon(k) &\leq \dfrac{c}{n}\sum_{k = -n+1}^{n-1}\abs{k}^q  \Upsilon(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} c\sum_{k = -n+1}^{n-1}\abs{k}^q  \Upsilon(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
\end{align*}

@@

Finally, we will solve for $P_2$. Note that $O_1 = (\abs{k}/n)\mathcal{O}(1/n)$ and $O_2 = \mathcal{O}(1/n)$. So,
  \begin{align*}
    P_2  & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{k}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
 \end{align*}

%
Using \eqref{eq:P1_decomp},\eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:bias_gsve},
\[
\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
\]
which completes the result.
%
 % We have shown that all, but one, terms are $o(1/b_n^q)$. Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms. This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu_g$ in our replicated autovariance estimator. Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu_g$ contributes only $o(1)$ terms. 
% \end{proof}
